Sun vs Shade leaves (WTCIII)

### 2015-04-01 markdown/wtc_sunshade.Rmd
made two plotting scripts for markdown multi panel plots
more updates to markdown

---
title: "Sun v Shade leaves (WTCIII)"
author: "Court Campany"
date: "March 17, 2015"
output: html_document
---
```{r knitr_options , include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=6,
echo=FALSE, message=FALSE,
fig.align='center', warning=FALSE)
```

@@

### <u>Mesophyll Conducatnce</u>

* We took leaf measurements at their current temperature (ambient, +3C) for paired comparisons across leaf types at a large range of temperatures.

* Sun leaves were taken from upper canopy at their current light level.  Shade leaves were taken from lower canopy, first at their current light level and then again at sun leaf PPFD.

@@

* For simplicity I have generalized most of the results below to just sun vs shade leaves (temperature not standardized).

* Further analysis is also needed to tease apart any effects of temperature treatment as data below are overall means across the 6 campaigns

####g<sub>m</sub> by leaf type and light environment

*  Below are means and standard errors of g<sub>m</sub> across all campaigns.

* Here I separated the well watered treatment from the drought treatment.  I'm more confident in the well watered values as I was often on the cutoff point with drawdown and xsi for drought leaves. They do show similar patterns but g<sub>m</sub> seems to be higher in drought trees

* Shade g<sub>m</sub> is always lower than sun leaves but when the lights are turned on they have in instantaneous response in g<sub>m</sub> that resembles sun leaves

@@

* This figure shows the instantaneous response of g<sub>m</sub> in shade leaves when the lights are 'turned on'

```{r gm lights on}
#plot low vs high light shade leaves
plot(Photo~gm, data=gm_water, subset=leaflight=="shade-high", pch=16, col=lightscol, ylim=c(0,25), xlim=c(0,.4), 
     xlab=gmlab, ylab="", cex=1.25)
  points(Photo~gm, data=gm_water, subset=leaflight=="shade-low",pch=16, col=shacol, cex=1.25)
  legend("topright", lightleg, pch=16,inset = 0.02, col=lightlab) 
  legend("topleft", "Shade Leaves", bty='n') 
  title(ylab=satlab, mgp=ypos, cex=1.2)
```

* Here is a simple version of the paired comparisons.  Only shade low light and sun leaves are used (watered and drought treatments together). All leaf types are compared to sun leaves at ambient temperature treatment (x axis)

@@

par(cex.axis=1.21, cex.lab=1.51,las=1,mgp=c(3.5,1,0),mfrow=c(3,1),  
    omi=c(.5,0,0.1,0.1))   
# First Panel
par(mar=c(0,7,2,2))
plot(gm_sp[[4]][,3]~gm_sp[[3]][,3], pch=21, bg=wa[3], cex=2.5, ylab="", xlab="", xlim=c(0,.5), ylim=c(0,.5),
     axes=FALSE) 
abline(0,1, lty=2)
axis(1, labels=FALSE) 
axis(2, labels=TRUE) 
box()
legend(.4,.45, pairlab[1], pch=21, pt.bg=paircol[1], pt.cex=2,bg="white",inset = 0.06)

# Second panel   
par(mar=c(0,7,0,2))
plot(gm_sp[[1]][,3]~gm_sp[[3]][,3], pch=21, bg=wa[1], cex=2.5, ylab=gmlab, xlim=c(0,.5), ylim=c(0,.5),xlab="",
     axes=FALSE)     
abline(0,1, lty=2)
legend(.4,.45, pairlab[2], pch=21, pt.bg=paircol[2], pt.cex=2,bg="white",inset = 0.06)
axis(1, labels=FALSE) 
axis(2, labels=TRUE) 
box()

#third panel
par(mar=c(5,7,0,2))
plot(gm_sp[[2]][,3]~gm_sp[[3]][,3], pch=21, bg=wa[5], cex=2.5, ylab="", xlim=c(0,.5), ylim=c(0,.5),xlab=suatgm)   
abline(0,1, lty=2)
legend(.4,.45, pairlab[3], pch=21, pt.bg=paircol[3], pt.cex=2,bg="white",inset = 0.06) 
```

* Here we see a slight reduction in g<sub>m</sub> with increase in temperature, but only in sun leaves

@@

### <u>Leaf Physiology</u>
* Below are figures of sun and shade leaf physiology, keeping it simple by ignoring the temperature treatment. We can address that later.

```{r A_gs}
##calculate CC
gmwet$Cc<- with(gmwet, Ci-Photo/gm)
gmwet$cc_ci<- with(gmwet, Ci/Cc)

###get average by id
gm_agg <- summaryBy(Photo+Cond+Ci+Cc+gm+VpdL+xsi+DELTA+cc_ci ~ chamber+id+leaf +light+temp+leaflight, 
                    data=gmwet, FUN=mean, keep.names=TRUE)

##remove shade-high
gm_sunsha <- gm_agg[gm_agg$leaflight != "shade-high",]
  gm_sunsha <- droplevels(gm_sunsha)
  gm_sunsha$id <- gsub("-high", "", gm_sunsha$id)
  gm_sunsha$id <- gsub("-low", "", gm_sunsha$id)

##merge
gm_c13 <- merge(gm_sunsha, Ci_bar[, c(2,8)], by="id")
  gm_c13$Cc_bar <- with(gm_c13, ci_bar-Photo/gm)

###Photosynthesis vs gs

  ####run gam models and then predict
  #SUN leaves
  sunmod <- gam(Photo ~ s(Cond, k=5), data=gm_c13, subset=leaflight=="sun-high")

  #predict
  #get apprpriate vector of gs from sun leaves
  gsdat <- gm_c13[gm_c13$leaflight=="sun-high", "Cond"]

  #generate sequence and then predict
  gssun_seq <- seq(min(gsdat), max(gsdat), length=101)
  gssun_pred <- predict(sunmod, newdata=data.frame(Cond=gssun_seq), se.fit=TRUE)

  #ci and model fit
  sunupr <- gssun_pred$fit + (2*gssun_pred$se.fit)
  sunlwr <- gssun_pred$fit - (2*gssun_pred$se.fit)

  #SHADE leaves
  shamod <- gam(Photo ~ s(Cond, k=5), data=gm_c13, subset=leaflight=="shade-low")

  #get apprpriate vector CC from sun leaves
  gsdat2 <- gm_c13[gm_c13$leaflight=="shade-low", "Cond"]
  #generate sequence and then predict
  gssha_seq <- seq(min(gsdat2), max(gsdat2), length=101)
  gssha_pred <- predict(shamod, newdata=data.frame(Cond=gssha_seq), type="link", se.fit=TRUE)

  shaupr <- gssha_pred$fit + (2*gssha_pred$se.fit)
  shalwr <- gssha_pred$fit - (2*gssha_pred$se.fit)

  ###plot
  plot(Photo~Cond, data=gm_c13, subset=leaflight=="sun-high", pch=16, col=suncol, ylim=c(0,25), 
       xlim=c(0,.4), xlab=condlab, ylab="", cex=1.25)

  lines(gssun_seq, sunupr, lty=2, lwd=2,col=suncol)
  lines(gssun_seq, sunlwr, lty=2, lwd=2,col=suncol)
  lines(gssun_seq, gssun_pred$fit, lty=1, lwd=2,col=suncol)

  #shade
  points(Photo~Cond, data=gm_c13, subset=leaflight=="shade-low", pch=16, col=shacol, cex=1.25)
  lines(gssha_seq, shaupr, lty=2, lwd=2,col=shacol)
  lines(gssha_seq, shalwr, lty=2, lwd=2,col=shacol)
  lines(gssha_seq, gssha_pred$fit, lty=1, lwd=2,col=shacol)

  title(ylab=satlab, mgp=ypos, cex=1.2)
  legend("topleft", leaflab2, pch=16,inset = 0.03, col=leafcol) 
```

```{r leafphys}
source("calculated_data/bootstrap/readboot.R")

###Photosynthesis vs gm
plot(Photo~gm, data=sundat, pch=16, col=suncol, ylim=c(0,25), xlim=c(0,.4), xlab=gmlab, ylab="", cex=1.25)
  points(Photo~gm, data=shadat, pch=16, col=shacol, cex=1.25)
with(agm_sun, {
  lines(gm, lcl, lty=2, lwd=2,col="forestgreen")
  lines(gm, ucl, lty=2, lwd=2,col="forestgreen")
  lines(gm, pred, lty=1, lwd=2,col="forestgreen")
})
with(agm_sha, {
  lines(gm, lcl, lty=2, lwd=2,col="yellow4")
  lines(gm, ucl, lty=2, lwd=2,col="yellow4")
  lines(gm, pred, lty=1, lwd=2,col="yellow4")
})
title(ylab=satlab, mgp=ypos, cex=1.2)
legend("topleft", leaflab2, pch=16,inset = 0.03, col=leafcol)

###Photosynthesis vs Ci
plot(Photo~Ci, data=sundat, pch=16, col=suncol, ylim=c(0,25), xlim=c(0,350), xlab=cilab, ylab="", cex=1.25)
points(Photo~Ci, data=shadat, pch=16, col=shacol, cex=1.25)
with(aci_sun, {
  lines(Ci, lcl, lty=2, lwd=2,col="forestgreen")
  lines(Ci, ucl, lty=2, lwd=2,col="forestgreen")
  lines(Ci, pred, lty=1, lwd=2,col="forestgreen")
})
with(aci_sha, {
  lines(Ci, lcl, lty=2, lwd=2,col="yellow4")
  lines(Ci, ucl, lty=2, lwd=2,col="yellow4")
  lines(Ci, pred, lty=1, lwd=2,col="yellow4")
})
title(ylab=satlab, mgp=ypos, cex=1.2)
legend("topleft", leaflab2, pch=16,inset = 0.03, col=leafcol)

 ###Photosynthesis vs Cc 
  plot(Photo~Cc, data=sundat, pch=16, col=suncol, ylim=c(0,25), xlim=c(0,350), xlab=cclab, ylab="", cex=1.25)
  points(Photo~Cc, data=shadat, pch=16, col=shacol, cex=1.25)
  with(acc_sun, {
    lines(Cc, lcl, lty=2, lwd=2,col="forestgreen")
    lines(Cc, ucl, lty=2, lwd=2,col="forestgreen")
    lines(Cc, pred, lty=1, lwd=2,col="forestgreen")
  })
  with(acc_sha, {
    lines(Cc, lcl, lty=2, lwd=2,col="yellow4")
    lines(Cc, ucl, lty=2, lwd=2,col="yellow4")
    lines(Cc, pred, lty=1, lwd=2,col="yellow4")
  })
  title(ylab=satlab, mgp=ypos, cex=1.2)
  legend("topleft", leaflab2, pch=16,inset = 0.03, col=leafcol) 
```

* Photosynthesis and Ci calculated from leaf ${\delta}$^13^C

```{r cibar}
###Photosynthesis vs cibar
plot(Photo~ci_bar, data=sundat, pch=16, col=suncol, ylim=c(0,25), 
     xlim=c(0,350), xlab=cibarlab2, ylab="", cex=1.25)
#shade
points(Photo~ci_bar, data=shadat, pch=16, col=shacol, cex=1.25)
  with(acib_sun, {
    lines(ci_bar, lcl, lty=2, lwd=2,col="forestgreen")
    lines(ci_bar, ucl, lty=2, lwd=2,col="forestgreen")
    lines(ci_bar, pred, lty=1, lwd=2,col="forestgreen")
  })
  with(acib_sha, {
    lines(ci_bar, lcl, lty=2, lwd=2,col="yellow4")
    lines(ci_bar, ucl, lty=2, lwd=2,col="yellow4")
    lines(ci_bar, pred, lty=1, lwd=2,col="yellow4")
  })
title(ylab=satlab, mgp=ypos, cex=1.2)
legend("topleft", leaflab2, pch=16,inset = 0.03, col=leafcol) 
```

### <u>Shade versus Sun leaves</u>

This set of figures attempts to show how sun and shade leaves were fundamentally different.

* ACi curves were measured at saturating light for both sun and shade leaves.

* Here are predicted ACi curves for leaf types with temperature treatments. Both Vc<sub>max</sub> and J<sub>max</sub> are reduced in shade leaves with little effect of the temperature treatment. ACi curves were taken once towards the end of the experiment on well watered trees.

#plot
plot(sunAT_sim$Ci, sunAT_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab=cilab, ylab="", type="l", lwd=2)
  points(sunET_sim$Ci, sunET_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  points(shaAT_sim$Ci, shaAT_sim$ALEAF, col="yellowgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2)
  points(shaET_sim$Ci, shaET_sim$ALEAF, col="yellowgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  legend("bottomright", leglab2, lty=c(1,2,1,2), lwd=2,col=colaci, pt.bg=col4,inset = 0.03)
  title(ylab=satlab, mgp=ypos)
```

@@

```{r,results='asis'}
##this has droughtleaves
palette(c("yellowgreen", "green4"))
par(mar=c(5,5,2,2))
plot(c13.mean ~ leafN_area.mean, data=leaftraits, pch=16, col=as.factor(leaf), ylim=c(-35,-25), 
                 xlim=c(1,3.5), cex=1.25, xlab=narealab, ylab=c13lab)
legend("bottomright", leaflab, pch=16, col=c("yellowgreen", "green4"),pt.cex=1.5,inset = 0.03)

* The second figure shows leaf mass area for each gas exchange campaign.  Surprisingly, not very different.

@@

 bar(par, c(leaf_type, month), parbar, col=c("yellowgreen", "green4"), xlab="", ylab="", ylim=c(0, 2000), 
     half.errbar=FALSE)
 title(ylab=parlab, mgp=ypos)

 ###LMA--------------------------------------------------------------------------------------------------
 lma <- read.csv("calculated_data/leaf_chemistry.csv")

@@

 bar(lma, c(leaf, Month), lmabar, col=c("yellowgreen", "green4"), xlab="", ylab="", ylim=c(0, 185), half.errbar=FALSE)
 title(ylab=lmalab, mgp=ypos)

>>>>

---
title: "Sun vs Shade leaves (WTCIII)"
author: "Court Campany"
date: "April 1, 2015"
output: html_document
---
```{r knitr_options , include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=6,
echo=FALSE, message=FALSE,
fig.align='center', warning=FALSE)
```

@@

#### <u>Design</u>
* WTCIII was a warming experiemnt with ambient and +3°C warming (n=6).  A drought manipulation was added in the last few months of the experiment.
* Sun leaves were measured in the upper canopy at their current PPFD.  Shade leaves were measured in the lower canopy, first at their current PPFD and then again at sun leaf PPFD.
* New fully expanded leaves were measured. Shade leaves were sampled into the middle canopy as the experiment progressed to avoid issues with leaf age.
* Leaf physiological measurements were taken at their current temperature (ambient, +3°C) for paired comparisons across leaf types. Thus, data below represent a large range of temperatures from ~18-35°C.
* For simplicity I have generalized most of the results below to just sun vs. shade leaves. So effects of the warming treatment are often not included and there is no standarizatiopn of leaf temperature.
* Unless it is explicitly stated I have left off the drought treatment as well.  
* Data below are mostly overall means across the 6 campaigns.  We can tease apart temperature/drought effects later.

#### <u>Were Sun and Shade leaves actually different?</u>

#plot
plot(sunAT_sim$Ci, sunAT_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab=cilab, ylab="", type="l", lwd=2, ylim=c(0,30))
  points(sunET_sim$Ci, sunET_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  points(shaAT_sim$Ci, shaAT_sim$ALEAF, col="yellow4", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2)
  points(shaET_sim$Ci, shaET_sim$ALEAF, col="yellow4", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  legend("bottomright", leglab2, lty=c(1,2,1,2), lwd=2,col=colaci, pt.bg=col4,inset = 0.03)
  title(ylab=satlab, mgp=ypos)
```

* ACi curves were measured at saturating light for both sun and shade leaves. 
* Here are predicted ACi curves for leaf types with temperature treatments. Both Vc<sub>max</sub> and J<sub>max</sub> are reduced in shade leaves with little effect of the temperature treatment. ACi curves were taken once towards the end of the experiment on well watered trees

#### <u>Mesophyll Conducatnce</u>

@@

#### g<sub>m</sub> by leaf type and light environment

* The two tables below are means and standard errors of g<sub>m</sub> across all campaigns.

* The well-watered treatment from the drought treatment are seperated.  I'm more confident in the well-watered values as I was often on the cutoff point with drawdown and xsi for drought leaves. They do show similar patterns but g<sub>m</sub> seems to be higher in drought trees

* Shade leaf g<sub>m</sub> is always lower than sun leaves but when the lights are 'turned on' they have in instantaneous response in g<sub>m</sub> that resembles sun leaves.

@@

```{r gm lights on}
#plot low vs high light shade leaves
plot(Photo~gm, data=gm_water, subset=leaflight=="shade-high", pch=16, col=lightscol, ylim=c(0,30), xlim=c(0,.4), 
     xlab=gmlab, ylab="", cex=1.25)
  points(Photo~gm, data=gm_water, subset=leaflight=="shade-low",pch=16, col=shacol, cex=1.25)
  legend("topright", lightleg, pch=16,inset = 0.02, col=lightlab) 
  legend("topleft", "Shade Leaves", bty='n') 
  title(ylab=satlab, mgp=ypos, cex=1.2)
```

* This figure shows the instantaneous response of g<sub>m</sub> in shade leaves when the lights are 'turned on'.

@@

par(cex.axis=1.21, cex.lab=1.51,las=1,mgp=c(3.5,1,0),mfrow=c(3,1),  
    omi=c(.5,0,0.1,0.1))   
# First Panel
par(mar=c(0,7,2,2))
plot(gm_sp[[4]][,3]~gm_sp[[3]][,3], pch=21, bg=wa[3], cex=2.5, ylab="", xlab="", xlim=c(0,.4), ylim=c(0,.4),
     axes=FALSE) 
abline(0,1, lty=2)
axis(1, labels=FALSE) 
axis(2, labels=TRUE) 
box()
legend(.3,.35, pairlab[1], pch=21, pt.bg=paircol[1], pt.cex=2,bg="white",inset = 0.06)

# Second panel   
par(mar=c(0,7,0,2))
plot(gm_sp[[1]][,3]~gm_sp[[3]][,3], pch=21, bg=wa[1], cex=2.5, ylab=gmlab, xlim=c(0,.4), ylim=c(0,.4),xlab="",
     axes=FALSE)     
abline(0,1, lty=2)
legend(.3,.35, pairlab[2], pch=21, pt.bg=paircol[2], pt.cex=2,bg="white",inset = 0.06)
axis(1, labels=FALSE) 
axis(2, labels=TRUE) 
box()

#third panel
par(mar=c(5,7,0,2))
plot(gm_sp[[2]][,3]~gm_sp[[3]][,3], pch=21, bg=wa[5], cex=2.5, ylab="", xlim=c(0,.4), ylim=c(0,.4),xlab=suatgm)   
abline(0,1, lty=2)
legend(.3,.35, pairlab[3], pch=21, pt.bg=paircol[3], pt.cex=2,bg="white",inset = 0.06) 
```

* Here is a simple version of the paired leaf comparisons.  Shade low light and sun leaves are used (watered and drought treatments are combined). Leaf types (with temperature treatment) are compared to sun leaves at ambient temperature as the control treatment (x axis).

@@

* This figure shows the relationship between g<sub>m</sub> and temperature with 95% confidence intervals.  Here we see a slight reduction in g<sub>m</sub> with increases in temperature, but only significant in sun leaves.

### <u>Sun vs. Shade Leaf Physiology</u>

```{r A_gs, fig.width=12, fig.height=6}
source("markdown/ags_plots.R")
```

* Figures of photosynthesis and g<sub>s</sub>.  Panel (a) is shown with 95% confidence intervals.  Panel (b) shows predicted photosynthesis rates generated with g<sub>s</sub> values, mean leaf temperature and PPFD (sun/shade), and ACi parameters including ambient and elevated temperature treatments. Here we can see optimal stomatal behaviour in sun leaves but not in shade leaves.

```{r a-gm, }
source("calculated_data/bootstrap/readboot.R")
  ###Photosynthesis vs gm
plot(Photo~gm, data=sundat, pch=16, col=suncol, ylim=c(0,30), xlim=c(0,.4), xlab=gmlab, ylab="", cex=1.25)
  points(Photo~gm, data=shadat, pch=16, col=shacol, cex=1.25)
with(agm_sun, {
  lines(gm, lcl, lty=2, lwd=2,col="forestgreen")
  lines(gm, ucl, lty=2, lwd=2,col="forestgreen")
  lines(gm, pred, lty=1, lwd=2,col="forestgreen")
})
with(agm_sha, {
  lines(gm, lcl, lty=2, lwd=2,col="yellow4")
  lines(gm, ucl, lty=2, lwd=2,col="yellow4")
  lines(gm, pred, lty=1, lwd=2,col="yellow4")
})
title(ylab=satlab, mgp=ypos, cex=1.2)
legend("topleft", leaflab2, pch=16,inset = 0.03, col=leafcol) 
```

* This figure shows the relationship between photosynthesis and g<sub>m</sub> for sun and shade leaves with 95% confidence intervals.

```{r leafphys,fig.width=12, fig.height=6}
###Photosynthesis vs Ci
  shade <- gm_c13[gm_c13$leaf=="shade",]
  sun <- gm_c13[gm_c13$leaf=="sun",]

  #read in jmax vcmax
  jvc<- read.csv("calculated_data/tdl_aci.csv")

  #simulate ACi curves for each leaf, ambient and elevated T
  sunAT_sim <- Aci(Ci=seq(50,1000,length=101), Vcmax=jvc[3,3], Jmax=jvc[3,4],PPFD=1407.959)
  sunET_sim <- Aci(Ci=seq(50,1000,length=101), Vcmax=jvc[4,3], Jmax=jvc[4,4], PPFD=1407.959)
  shaAT_sim <- Aci(Ci=seq(50,1000,length=101), Vcmax=jvc[1,3], Jmax=jvc[1,4], PPFD=305)
  shaET_sim <- Aci(Ci=seq(50,1000,length=101), Vcmax=jvc[2,3], Jmax=jvc[2,4],PPFD=305)

par(cex.axis=.96, cex.lab=1.2,mfrow=c(1,2),oma=c(0.1,0.1,0.1,0.1), las=1)

par(mar=c(5,4,2,0))
plot(Photo~Ci, data=sundat, pch=16, col=suncol, ylim=c(0,30), xlim=c(0,350), xlab=cilab, ylab="", cex=1.25)
points(Photo~Ci, data=shadat, pch=16, col=shacol, cex=1.25)
with(aci_sun, {
  lines(Ci, lcl, lty=2, lwd=2,col="forestgreen")
  lines(Ci, ucl, lty=2, lwd=2,col="forestgreen")
  lines(Ci, pred, lty=1, lwd=2,col="forestgreen")
})
with(aci_sha, {
  lines(Ci, lcl, lty=2, lwd=2,col="yellow4")
  lines(Ci, ucl, lty=2, lwd=2,col="yellow4")
  lines(Ci, pred, lty=1, lwd=2,col="yellow4")
})
title(ylab=satlab, mgp=ypos, cex=1.2)
legend("topright", leaflab2, pch=16,inset = 0.03, col=leafcol) 
text(x=.01, 29.5, "(a)", cex=1.2)

par(mar=c(5,2.5,2,2)) 
plot(sunAT_sim$Ci, sunAT_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab=cilab, ylab="", type="l",  lwd=2,ylim=c(0,30), xlim=c(0,1000))
  points(sunET_sim$Ci, sunET_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  points(shaAT_sim$Ci, shaAT_sim$ALEAF, col="yellow4", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2)
  points(shaET_sim$Ci, shaET_sim$ALEAF, col="yellow4", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  points(Photo~Ci, data=sundat, pch=16, col=suncol, cex=1.25)
  points(Photo~Ci, data=shadat, pch=16, col=shacol, cex=1.25)

  legend("bottomright", leglab2, lty=c(1,2,1,2), lwd=2,col=colaci, pt.bg=col4,inset = 0.03)
  text(x=.01, 29.5, "(b)", cex=1.2)
```

* These figures show the relationship of photosynthesis to Ci. Panel (a) has 95% confidence intervals.  Panel (b) has the predicted ACi curves using the biochemical parameters measured at saturating light but fitted with mean PPFD of sun and shade leaves.

```{r}
 ###Photosynthesis vs Cc 
  plot(Photo~Cc, data=sundat, pch=16, col=suncol, ylim=c(0,30), xlim=c(0,350), xlab=cclab, ylab="", cex=1.25)
  points(Photo~Cc, data=shadat, pch=16, col=shacol, cex=1.25)
  with(acc_sun, {
    lines(Cc, lcl, lty=2, lwd=2,col="forestgreen")
    lines(Cc, ucl, lty=2, lwd=2,col="forestgreen")
    lines(Cc, pred, lty=1, lwd=2,col="forestgreen")
  })
  with(acc_sha, {
    lines(Cc, lcl, lty=2, lwd=2,col="yellow4")
    lines(Cc, ucl, lty=2, lwd=2,col="yellow4")
    lines(Cc, pred, lty=1, lwd=2,col="yellow4")
  })
  title(ylab=satlab, mgp=ypos, cex=1.2)
  legend("topleft", leaflab2, pch=16,inset = 0.03, col=leafcol) 
```

* This figures show the relationship of photosynthesis to Cc with 95% confidence intervals, calculated with g<sub>m</sub> data

### <u>Shade versus Sun leaves, continued</u>

This next set of figures attempts to show how sun and shade leaves were fundamentally different.

```{r,results='asis'}
##this has droughtleaves
palette(c("yellow4", "forestgreen"))
par(mar=c(5,5,2,2))
plot(c13.mean ~ leafN_area.mean, data=leaftraits, pch=16, col=as.factor(leaf), ylim=c(-35,-25), 
                 xlim=c(1,3.5), cex=1.25, xlab=narealab, ylab=c13lab)
legend("bottomright", leaflab, pch=16, col=c("yellow4", "green4"),pt.cex=1.5,inset = 0.03)

@@

@@

 bar(par, c(leaf_type, month), parbar, col=c("yellow4", "forestgreen"), xlab="", ylab="", ylim=c(0, 2000), 
     half.errbar=FALSE)
 title(ylab=parlab, mgp=ypos)
```

```{r}
 ###LMA-
 lma <- read.csv("calculated_data/leaf_chemistry.csv")

@@

 bar(lma, c(leaf, Month), lmabar, col=c("yellow4", "forestgreen"), xlab="", ylab="", ylim=c(0, 185), half.errbar=FALSE)
 title(ylab=lmalab, mgp=ypos)
```

* This figure shows leaf mass area for each gas exchange campaign.  Surprisingly, not very different between leaf types.
